
This chapter includes the specifications for all of the Role/System pair interfaces depicted in figure~\ref{fig:UCDTopLevel} on page~\pageref{fig:UCDTopLevel}.
Each interface section first outlines the purpose the interface serves.
Core functionality for each interface is exposed through the attribute functions (see section \ref{sec:Attributes}).
Each interface section includes a table of the supported attributes for that interface. 
The table contains the \textit{suggested} attributes that the implementation should support for each interface. 
The implementation can choose to implement additional, some subset, or none of the attributes listed for that interface.
As previously mentioned, the implementation must implement all attribute functions whether individual attributes are supported or not.
If a particular attribute is not supported for that interface the implementation should return \texttt{PWR_RET_NOT_IMPLEMENTED}.

In addition to the attribute functions, other Core (Common) functions are included in this specification.
Each individual interface section will enumerate the Core (Common) functions that the specification suggests are applicable for that interface (see chapter \ref{chap:Common} for details regarding Core (Common) functions).
Again, the implementation must implement these functions but may choose not to support them for a particular interface.

Each section also includes the High-Level (Common) functions that are applicable to that section (see chapter \ref{chap:HighLevel} for details regarding High-Level (Common) functions).
These functions are functions that are applicable to more than one Role/System pair interface.

Finally, individual interface sections may also contain interface specific functions.
These are functions that, at the time of their addition to the specification, are specific to one Role/System pair. 
This does not indicate that the function cannot be supported by an implementation for other Role/System pairs, only that the authors did not recognize a use for other interfaces at the time of addition to the specification.



\section{Operating System, Hardware Interface}\label{sec:OSHW}
\input{OSHW}

\newpage
\section{Monitor and Control, Hardware Interface}\label{sec:MCHW}
\input{MCHW}

\newpage
\section{Application, Operating System Interface}\label{sec:AppOS}
\input{AppOS}

\newpage
\section{User, Resource Manager Interface}\label{sec:UserRM}
\input{UserRM}

\newpage
\section{Resource Manager, Operating System Interface}\label{sec:RMOS}
\input{RMOS}

\newpage
\section{Resource Manager, Monitor and Control Interface}\label{sec:RMMC}
\input{RMMC}

\newpage
\section{Administrator, Monitor and Control Interface}\label{sec:AdminMC}
\input{AdminMC}

\newpage
\section{HPCS Manager, Resource Manager Interface}\label{sec:MgrRM}
\input{MgrRM}

\newpage
\section{Accounting, Monitor and Control Interface}\label{sec:AccMC}
\input{AccMC}

\newpage
\section{User, Monitor and Control Interface}\label{sec:UserMC}
\input{UserMC}

